\LARGE \bf Preparation of Papers for IEEE Sponsored Conferences \& Symposia*

### 2017-04-08 pwarel.tex
.

\begin{definition}[Graph Abstraction]
    The quantization function $Q_\epsilon$ induces a DAG on the discrete
    abstraction given by a graph $G(V, E)$, where each vertex
    corresponds to a cell $V_i = C_i$, and an edge exists between two
    cells $(C_j, C_k) \in E$ iff there exist state-input pairs
    $(\vx,\vu) \in C_j$, $(\vx', \vu) \in C_k$ such that $\vx =
    \simulate(\vx, \vu )$.
\end{definition}

@@

Recall that each edge $(C,C')$ of the graph $G$ denotes an observed
trajectory segment between the respective cells. The graph abstraction
$G$ only states that there exists a state $\x \in C$ from which the
system can evolve to a future state $\x' \in C'$. To increase the
precision we iteratively refined the abstraction by state
splitting. Instead, we now propose an `enrichment' $G^R$ of $G$ by computing a
set of local relations $R_{(C,C')}(\x,\x')$ for every edge $(C,C')$,
which non-deterministically describe relations between $\x \in C$ and $\x'
\in C'$. This is illustrated in \figref{enriched-edge}.
%(compare with \figref{segtraj}).

The enriched graph $G^R$ captures the underlying local forward
dynamics describing the evolution of the system in each abstract
state. We represent the dynamics using an affine model with an
interval error. Such a model can either be approximated using learning
methods or computed as a sound (over) approximation using reachability
set computation methods. Because we assume black box semantics, we
only present the former. Using regression analysis on the $start$ and
$end$ states of the witnessed trajectory segments between two cells,
we compute an approximate discrete map along with an error estimate.
Moreover, using the simulation function $\simulate$, additional
trajectory segments (or data) can be generated if required. The data
can be separated into a training set and testing set to compute the
map and the error respectively.  The latter case can be explored if
the symbolic dynamics of the system are known. A tool like
\flowstar~\cite{chen2013flow} can be used to find the reachable set
map.

@@

Instead of using a CEGAR like loop (used in~\cite{zutshi2014multiple}),
we use the generated trajectory segments to learn quantitative models
describing the local behavior of the system. These models are defined
by a set of relations $R \subseteq \HybridStates \times \HybridStates$
for each edge of the reachability graph.

>>>>

\begin{definition}[Graph Abstraction]
    The quantization function $Q_\epsilon$ induces a DAG on the discrete
    abstraction given by a graph $G(V, E)$, where each vertex
    corresponds to a cell $V_i = C$, and an edge exists between two
    cells $(C, C') \in E_i$ iff there exist state-input pairs
    $(\vx,\vu) \in C$, $(\vx', \vu) \in C'$ such that $\vx' =
    \simulate(\vx, \vu )$.
\end{definition}

@@

Recall that each edge $(C,C')$ of the graph $G$ denotes an observed
trajectory between the respective cells. The graph abstraction
$G$ only states that there exists a state $\x \in C$ from which the
system can evolve to a future state $\x' \in C'$. To increase the
precision we iteratively refined the abstraction by state
splitting. Instead, we now propose an `enrichment' $G^R$ of $G$ by computing a
set of local relations $R_{(C,C')}(\x,\x')$ for every edge $(C,C')$,
which non-deterministically describe relations between $\x \in C$ and $\x'
\in C'$. This is illustrated in \figref{enriched-edge}.
%(compare with \figref{segtraj}).

The enriched graph $G^R$ captures the underlying local forward
dynamics describing the evolution of the system in each abstract
state. We represent the dynamics using an affine model with an
interval error. Such a model can either be approximated using learning
methods or computed as a sound (over) approximation using reachability
set computation methods. Because we assume black box semantics, we
only present the former. Using regression analysis on the $start$ and
$end$ states of the witnessed trajectory between two cells,
we compute an approximate discrete map along with an error estimate.
Moreover, using the simulation function $\simulate$, additional
trajectories (or data) can be generated if required. The data
can be separated into a training set and testing set to compute the
map and the error respectively.  The latter case can be explored if
the symbolic dynamics of the system are known. A tool like
\flowstar~\cite{chen2013flow} can be used to find the reachable set
map.

@@

Instead of using a CEGAR like loop (used in~\cite{zutshi2014multiple}),
we use the generated trajectories to learn quantitative models
describing the local behavior of the system. These models are defined
by a set of relations $R \subseteq \HybridStates \times \HybridStates$
for each edge of the reachability graph.
